fauxpas
=======

```{r echo=FALSE}
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines) == 1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL,
            x[lines],
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![Build Status](https://travis-ci.org/sckott/fauxpas.svg)](https://travis-ci.org/sckott/fauxpas)
[![codecov.io](https://codecov.io/github/sckott/fauxpas/coverage.svg?branch=master)](https://codecov.io/github/sckott/fauxpas?branch=master)

`fauxpas` does http errors

The plan is:

* HTTP error classes more in line with Ruby/Python/Etc.
* An error class for each HTTP error in case a user wants to 
be specific to an HTTP error, and general purpose handlers 
for any error
* Work with any of the major R http clients: `httr`, `curl`, `RCurl` - 
so use probably S3 dispatch to handle inputs from those clients 
appropriately
* Provide flexiblity for what to do on an HTTP error, including 
custom functions

## Install

```{r eval=FALSE}
devtools::install_github("sckott/fauxpas")
```

```{r}
library("fauxpas")
```

## use with httr

```{r eval=FALSE}
library("httr")
res <- GET("https://httpbin.org/status/414")
error_414(res)
#> Error in tmp$do(x) : Request-URI Too Long (HTTP 414).
#> The server is refusing to service the request because the Request-URI is
#>    longer than the server is willing to interpret. This rare condition is only likely
#>    to occur when a client has improperly converted a POST request to a GET request
#>    with long query information, when the client has descended into a URI black hole
#>    of redirection (e.g., a redirected URI prefix that points to a suffix of itself),
#>    or when the server is under attack by a client attempting to exploit security
#>    holes present in some servers using fixed-length buffers for reading or
#>    manipulating the Request-URI.
```

## Meta

* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
