fauxpas
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>",
  eval = TRUE
)
```

[![R-check](https://github.com/sckott/fauxpas/actions/workflows/R-check.yml/badge.svg?branch=main)](https://github.com/sckott/fauxpas/actions/workflows/R-check.yml)
[![cran checks](https://badges.cranchecks.info/worst/fauxpas.svg)](https://github.com/sckott/fauxpas)
[![cran version](http://www.r-pkg.org/badges/version/fauxpas)](https://cran.r-project.org/package=fauxpas)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/fauxpas)](https://github.com/r-hub/cranlogs.app)

`fauxpas` does http errors

* HTTP error classes more in line with Ruby/Python/Etc.
* An error class for each HTTP status in case a user wants to
be specific to an HTTP status code, and general purpose handlers
for any error
* Work with any of the major R http clients: `crul`, `curl`, `httr`, (maybe
`RCurl` later)
* Provide flexiblity for what to do on an HTTP error, including
custom functions and message templates

Info Links:

* HTTP on wikipedia: <https://en.wikipedia.org/wiki/Hypertext_Transfer_Protocol>
* HTTP2 on wikipedia: <https://en.wikipedia.org/wiki/HTTP/2>
* HTTP/1.1: <https://www.w3.org/Protocols/rfc2616/rfc2616-sec10.html>
* HTTP/2: <https://datatracker.ietf.org/doc/html/rfc7540>

## Install

CRAN version

```{r eval=FALSE}
# install.packages("pak")
pak::pak("fauxpas")
```

Dev version

```{r eval=FALSE}
pak::pak("sckott/fauxpas")
```

```{r}
library("fauxpas")
```

## use with crul

```{r}
library("crul")
cli <- HttpClient$new("https://httpbin.org/status/414")
res <- cli$get()
http(res)
http414(res)
```

```{r}
x <- HTTPRequestURITooLong$new()
x$do_verbose(res)
```

## use with curl

```{r}
library("curl")
h <- curl::new_handle()
curl::handle_setopt(h)
resp <- curl::curl_fetch_memory("https://httpbin.org/status/404", h)
http(resp)
http404(resp)
```

```{r}
x <- HTTPNotFound$new()
x$do_verbose(resp)
```

## use with httr

```{r}
library("httr")
res <- GET("https://httpbin.org/status/405")
http405(res)
```

```{r}
x <- HTTPMethodNotAllowed$new()
x$do_verbose(res)
```

## Meta

* Please [report any issues or bugs](https://github.com/sckott/fauxpas/issues)
* License: MIT
* Get citation information for `fauxpas` in R doing `citation(package = 'fauxpas')`
* Please note that the fauxpas project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
